Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-28 ms.tex
address comment about first paragraph of fitting procedure section

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. In the case of our full-resolution $6.1'$ fits, these parameters
are the SED normalization and the hot dust temperature $T_2$. The same 
formalism will apply to our lower-resolution fits in which $f_1$ is also 
allowed to vary from one line of sight to another.

>>>>

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. We perform two types of fits: (1) full-resolution 
$6.1'$ fits, in which just two parameters, the SED normalization and the hot 
dust temperature $T_2$, vary spatially and (2) lower-resolution fits in which 
$f_1$ is also allowed to vary from one line of sight to another.
